Supplementary Information

### 2020-06-06 doc/manuscript/MEE_manuscript.Rmd
switched presentation order, putting climate ahead of tree size

### Length planning:
## Main text ~4300 words --> ~28 paragraphs averaging 150 words
# Intro- 900/ 6
# Methods- 1500 / (11)
# Results - 1000/ (6)
# Discussion - 900 / (5)
## References: figure ~40 words each, so 50 refs = 2000
## Display items: figure ~100 words for each caption = 700 words
# Table1- table of sites
# Fig1- schematic illustrating our process
# Fig2- relationship of ∆r and ∆AGB to DBH (all site-species combinations)
# Fig3- climate senstivity (SCBI example): (a) Helcoski quilt plot, (b) Climwin panel a, (c) GLS output
# Fig4- multipanel- GLS results for climate sensitivity at all sites (3 columns with the 3 variable type groupings, 1 row per site)
# Fig5/ table2- DBH/climate interactions
# Fig 6/7- responses to CO2 and atmospheric deposition

@@

**Here, develop a new method that allows simultaneous consideration of the effects of tree size, objectively determined principle climate drivers, and other environemntal drivers on annual tree growth.** 
This allows us to ask:
(1) How do radial growth and aboveground biomass increments ($\Delta AGB$) vary with DBH?
(2) What are the most important climate drivers of annual growth, and over which time windows?
(3) What is the shape of the relationship between annual growth and climate drivers?
(4) Are there interactions between DBH and climate drivers common?
(5) How is growth simultaneously influenced by DBH, climate, and other environemental drivers (CO2, atmospheric deposition)?

@@

![**Figure 2 | Growth sensitivity to DBH:** (a) $\Delta r$, (b) $\Delta AGB$. THIS FIGURE IS JUST A SKETCH TO SHOW VALENTINE WHAT I HAVE IN MIND.](tables_figures/size_figure_sketch.png)

@@

![**Figure 3 | Example comparison of climate sensitivity derived via traditional methods (**a**) and our approach (**b-f**).** Example is for the sensitivity of 14 species at SCBI (codes given in Table S1) to potential evapotranspiration (PET), identified by both traditional methods and our method to be among the top climate drivers. Panel (**a**) shows a matrix of Pearson correlations between ring- width index and monthly climate variables. Panels (**b-d**) give statistics for time windows tested in *climwin*, where window open and close indicate months prior to current August, and cells across the lower diaganol indicate single-month tests (akin to panel **a**). Panels (**b**) and (**c**) give values of linear and quadratic terms for each time window, and (**d**) gives the $\Delta AIC$ for each. The time window with the minimum $\Delta AIC$ (0-3 months prior to August, or May-Aug; black boxes), was identified as the optimal window. Panel (**e**) shows the correlation of individual-level residuals to PET, with the function fit in *climwin*. Finally, panel (**f**) shows GLS model output, where PET is one of several driver variables (*specify model*). Plotted are responses of species for which PET was identified as a signficant driver in the top model.](tables_figures/climate_figure_sketch.png)

@@

![**Figure 4 | Climate senstivity for all sites.** Columns include the top variables in each grouping, with PET placed in the temperature group if identified as the top variable for both the temperature and cloudiness groups. For each species, relationships are plotted if included in top model. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD. (THIS FIGURE IS JUST A SKETCH TO SHOW VALENTINE WHAT I HAVE IN MIND.) ](tables_figures/climate_figure2_sketch.png)

>>>>

### Length planning:
## Main text ~4300 words --> ~28 paragraphs averaging 150 words
# Intro- 900/ 6
# Methods- 1500 / (11)
# Results - 1000/ (6)
# Discussion - 900 / (5)
## References: figure ~40 words each, so 50 refs = 2000
## Display items: figure ~100 words for each caption = 700 words
# Table1- table of sites
# Fig1- schematic illustrating our process
# Fig2- climate senstivity (SCBI example): (a) Helcoski quilt plot, (b) Climwin panel a, (c) GLS output
# Fig3-  multipanel- GLS results for climate sensitivity at all sites (3 columns with the 3 variable type groupings, 1 row per site) 
# Fig4-relationship of ∆r and ∆AGB to DBH (all site-species combinations)
# Fig5/ table2- DBH/climate interactions
# Fig 6/7- responses to CO2 and atmospheric deposition

@@

**Here, develop a new method that allows simultaneous consideration of the effects of tree size, objectively determined principle climate drivers, and other environemntal drivers on annual tree growth.** 
This allows us to ask:
(1) What are the most important climate drivers of annual growth, and over which time windows?
(2) What is the shape of the relationship between annual growth and climate drivers?
(3) How do radial growth and aboveground biomass increments ($\Delta AGB$) vary with DBH?
(4) Are there interactions between DBH and climate drivers common?
(5) How is growth simultaneously influenced by DBH, climate, and other environemental drivers (CO2, atmospheric deposition)?

@@

@@

![**Figure 2 | Example comparison of climate sensitivity derived via traditional methods (**a**) and our approach (**b-f**).** Example is for the sensitivity of 14 species at SCBI (codes given in Table S1) to potential evapotranspiration (PET), identified by both traditional methods and our method to be among the top climate drivers. Panel (**a**) shows a matrix of Pearson correlations between ring- width index and monthly climate variables. Panels (**b-d**) give statistics for time windows tested in *climwin*, where window open and close indicate months prior to current August, and cells across the lower diaganol indicate single-month tests (akin to panel **a**). Panels (**b**) and (**c**) give values of linear and quadratic terms for each time window, and (**d**) gives the $\Delta AIC$ for each. The time window with the minimum $\Delta AIC$ (0-3 months prior to August, or May-Aug; black boxes), was identified as the optimal window. Panel (**e**) shows the correlation of individual-level residuals to PET, with the function fit in *climwin*. Finally, panel (**f**) shows GLS model output, where PET is one of several driver variables (*specify model*). Plotted are responses of species for which PET was identified as a signficant driver in the top model.](tables_figures/climate_figure_sketch.png)

@@

![**Figure 3 | Climate senstivity for all sites.** Columns include the top variables in each grouping, with PET placed in the temperature group if identified as the top variable for both the temperature and cloudiness groups. For each species, relationships are plotted if included in top model. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD. (THIS FIGURE IS JUST A SKETCH TO SHOW VALENTINE WHAT I HAVE IN MIND.) ](tables_figures/climate_figure2_sketch.png)

![**Figure 4 | Growth sensitivity to DBH:** (a) $\Delta r$, (b) $\Delta AGB$. THIS FIGURE IS JUST A SKETCH TO SHOW VALENTINE WHAT I HAVE IN MIND.](tables_figures/size_figure_sketch.png)
